He-Man: A domain-specific language for lightweight concurrency

### 2012-03-07 paper/paper.tex
Update arg packet stuff in paper.

\begin{figure}[ht]
\centering
\begin{code}
class ArgPacket a b | a -> b, b -> a where
  toIExprList :: a -> [IExpr]
  makeVars :: [String] -> a
class ArgDecls a b | a -> b, b -> a where
  toITypeList :: a -> [IType]

instance ArgPacket (Expr a) [a] where
  toIExprList (E x) = [x]
  makeVars [x] = E (Var x)
instance ArgPacket (Expr a, Expr b) (a, b) where
  toIExprList (E x1, E x2) = [x1, x2]
  makeVars [x1, x2] = (E (Var x1), E (Var x2))
-- ...

instance ArgDecls (Type a) [a] where
  toITypeList t1 = [toIType t1]
instance ArgDecls (Type a, Type b) (a, b) where
  toITypeList (t1, t2) = [toIType t1, toIType t2]
-- ...

declare_thread :: (ArgPacket a c, ArgDecls b c) =>
                  b -> (a -> Prog ()) ->
                  ThreadCode c
declare_thread = ...
spawn :: ArgPacket a b => ThreadCode b -> a ->
                          Prog ()
spawn = ...
call :: ArgPacket a b => Prim -> Type c -> a ->
                         Prog (Expr c)
call = ...

>>>>

\begin{figure}[ht]
\centering
\begin{code}
class ArgPacket exps tys | exps -> tys,
                           tys -> exps where
  toIExprList :: exps -> [IExpr]
  makeVars :: [String] -> exps
  toITypeList :: tys -> [IType]

instance ArgPacket (Expr a) (Type a) where
  toIExprList (E e) = [e]
  makeVars [x] = E $ Var x
  toITypeList t = [toIType t]
instance ArgPacket (Expr a, Expr b) (Type a, Type b) where
  toIExprList (E e1, E e2) = [e1, e2]
  makeVars [x1, x2] = (E $ Var x1, E $ Var x2)
  toITypeList (t1, t2) = [toIType t1, toIType t2]
-- ...

declare_thread :: (ArgPacket exps tys) =>
                  tys -> (exps -> Prog ()) ->
                  ThreadCode exps
declare_thread = ...
spawn :: ArgPacket exps tys =>
         ThreadCode exps -> exps ->
         Prog ()
spawn = ...
call :: ArgPacket exps tys =>
        Prim -> Type c -> exps ->
        Prog (Expr c)
call = ...
